{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-05-30 thesis/education.tex
write abt pintos recruiting/retrospect

@@

For this study students were recruited remotely via email.
After each of the {\em threads} and {\em userprog} project deadlines (\sect{\ref{sec:overview-pintos}}),
% TODO talk about th econtence of the email

@@

>>>>

\subsection{Retrospect}

Landslide is great and should be used in 410. Dave wants to use it. That's enough evidence right there.

@@

For this study students were recruited remotely via email.
After each of the {\em threads} and {\em userprog} project deadlines (\sect{\ref{sec:overview-pintos}}),
\uchos staff sent students an email inviting them to volunteer to receive Landslide's bug reports,
disclaiming that it did not represent part of the official grading process but could help improve their future submissions.

@@

\subsection{Retrospect}

I attribute the low participation rate of Pintos students to P2 students to two major factors:
one, not incentivizing the students to directly improve their grades
(instead offering only the vague promise of a ``learning experience'' debugging their code only after handin),
and two, not traveling to the university to introduce the research topic in an in-person lecture
(leaving the students potentially confused about what advantage, if any, was offered over stress testing).

While part of the point of this experimental design was to evaluate Landslide as a grading tool in the hands of TAs,
I would be remiss to mention that I also feared the automatic annotation process would not be as robust as the P2 version.
Indeed, while helping Kevin get oriented with using Landslide,
I implemented
several % TODO: how many and what specifically
fixes/improvements to the setup scripts
as we found student kernels that failed to automatically annotate
(for example, those with {\tt ready\_list} changed to an array,
as described in \sect{\ref{sec:education-pintos-instrumentation}}).
Had we given Landslide directly to students that semester,
the students themselves would have had to email me for tech support.

Hypothetically, I could have achieved greater user study participation
either by offering extra credit to students
or by offering an autograder-like interface for students to receive bug reports before their deadlines instead of after
(either way requiring a more rigorous IRB review process).
Practically, as for non-research use in Pintos classes,
Landslide can now handle a considerably wider variety of student implementation quirks
on account of this time's fixes.
In its current shape I would recommend it for TA use grading,
but not necessarily directly to students without someone familiar with the codebase on immediate hand for tech support.

% Point two is much more easily addressed, although perhaps not necessary if only being used for grading anyway.
